---
title: "Challenge_1_Code"
date: "2025-04-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Challenge

In this challenge, you are required to estimate Euler's number \( e \) using its series expansion.

## Challenge Description

Construct an R function that can compute the value of \( e \) to at least five decimal places. The function should rely on the series expansion method.

## Method

You will need to implement the series expansion \( e = \sum_{n=0}^{\infty} \frac{1}{n!} \) in R, making use of loops to sum the terms of the series until additional terms do not change the result significantly.

## Code

```{r}
estimate_e <- function() {
  e_estimate <- 0
  n <- 0
  term <- 1  # Start with 1/0!
  
  repeat {
    e_estimate <- e_estimate + term
    n <- n + 1
    term <- term / n  # Compute the next term in the series, which is 1/n!
    
    if (term < .Machine$double.eps) break  # Break if the term is less than the smallest representable positive number
  }
  
  return(e_estimate)
}

# Test the function
estimated_e <- estimate_e()
print(paste("Estimated e:", estimated_e))
```